Longitudinal Manifold Estimation

### 2023-02-15 paper/main.tex
relocate algorithm, rearrange package calls

\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
%\RequirePackage[numbers]{natbib}
\RequirePackage[authoryear]{natbib}%% uncomment this for author-year citations
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}%% uncomment this for coloring bibliography citations and linked URLs
\RequirePackage{graphicx}%% uncomment this for including figures

\usepackage{amsmath, amssymb, amscd, amsthm, amsfonts}
\usepackage{graphicx}
\usepackage[perpage,symbol*]{footmisc}
\usepackage{float}
\usepackage{hyperref}
\usepackage{color}  
\usepackage{tikz}

@@

@@

The notation below is used to build to a definition of principal manifolds [still need to formally write out]:
\begin{itemize}
  \item Observed data $\left\{x_i\right\}_{i=1}^I \subset \mathbb{R}^D$
  \item Associated latent parameterizations $\left\{t_i\right\}_{i=1}^I \subset \mathbb{R}^d$
  \item $C_{\infty}\left(\mathbb{R}^d \to \mathbb{R}^D\right) = \left\{f \in C(\mathbb{R}^d \to \mathbb{R}^D): \lim_{\|t\|_{\mathbb{R}^d} \to \infty} \|f(t)\|_{\mathbb{R}^D} = \infty\right\}$ 
  \item $\nabla f$ denotes the gradient of $f$
  \item $\nabla^{\bigotimes 2}f$ denotes the Hessian matrix of $f$
  \item $\|\nabla^{\bigotimes 2}f\|_{\mathbb{R}^{d \times d}} = \left(\sum_{i, j = 1}^{d} |\frac{\partial^2f}{\partial t_i \partial t_j}(t)|^2\right)^{\frac{1}{2}}$
  \item $\|\nabla^{\bigotimes 2}f\|_{L^2(\mathbb{R}^{d})}^2 = \sum_{l = 1}^{D}\|\nabla^{\bigotimes 2}f_l\|_{L^2(\mathbb{R}^{d})}^2 = \sum_{l=1}^{D}\int_{\mathbb{R}^d}\sum_{i,j = 1}^{d}|\frac{\partial^2f_l}{\partial t_i \partial t_j}(t)|^2dt$ represents the total squared curvature of manifold $M_f^{d}$
  \item $\mathcal{K}_{\lambda, \mathbb{P}}(f, g) = \mathbb{E}\|X - f(\pi_{g}(X))\|_{\mathbb{R}^{D}}^2 + \lambda\|\nabla^{\bigotimes 2}f\|_{L^2(\mathbb{R}^{d})}^2$, with $\mathcal{K_{\lambda, \mathbb{P}}}(f) = \mathcal{K}_{\lambda, \mathbb{P}}(f, f)$
  \item A manifold $M_{f^*}^{d}$ determined by $f^*$ is a principal manifold for random $D$-vector $X$ with compact support $\text{supp}(\mathbb{P})$ with the tuning parameter $\lambda$ if \[%
    f_{\lambda}^{*} = \arg \min_{f \in \mathcal{F}(\mathbb{P})}\mathcal{K}_{\lambda, \mathbb{P}}(f)
  ,\]%
    where \[%
      \mathcal{F}(\mathbb{P}) = \left\{f \in C_{\infty} \cap \nabla^{-biot 2}L^2(\mathbb{R}^{d} \to \mathbb{R}^{D}): \sup_{x \in \text{supp}(\mathbb{P})}\|\pi_f(x)\|_{\mathbb{R}^{d}} = 1\right\}
    .\]%
  \item $\pi_{f_\lambda^{*}}(X)$ gives a $d$-dimensional parameterization of $X$
\end{itemize}

Given this definition, we now summarize the estimation method provided. This algorithm has three main steps: data reduction, fitting, and tuning. In the reduction step, the HDMDE algorithm is used to summarize the data $\left\{x_i\right\}_{i=1}^{I}$ by points $\left\{\mu_j\right\}_{j=1}^{N}$ with $N \leq I$, and each $\mu_j$ associated with weight $\theta_j$. The fitting stage of the algorithm finds estimated functions 
\[%
  \hat{f}_\lambda = \arg\min_f \mathcal{K}_{\lambda, \hat{Q}_N}(f)
,\]%
where 
\[%
  \mathcal{K}_{\lambda, \hat{Q}_N}(f) = \sum_{j = 1}^{N}\theta_j \|\mu_j - f(\pi_f(\mu_j))\|_{\mathbb{R}^{D}}^2 + \lambda\|\nabla^{\bigotimes 2}f\|_{L^2(\mathbb{R}^{d})}^2
\]% 
approximates $\mathcal{K}_{\lambda, \mathbb{P}}(f)$. The tuning stage chooses $\lambda^{*} = \arg\min_{\lambda > 0}(\mathcal{D}(\hat{f}_\lambda))$, where 
\[%
  \mathcal{D}(\hat{f}_\lambda) = \frac{1}{I}\sum_{i=1}^{I}\|x_i - \hat{f}_\lambda(\pi_{\hat{f}_\lambda}(x_i))\|_{\mathbb{R}^{D}}^2
.\]%

@@

Let $\{x_{it}\}_{i=1, t=1}^{I, T}$ be data points in $D$-dimensional space.

Outline:
\begin{enumerate}
    \item Introduce principal surfaces / principal manifolds, PME algorithm, and the loss function it minimizes
    \item Show updated loss function for LPME algorithm
    \item LPME algorithm
\end{enumerate}

@@

\begin{algorithm}
\caption{Longitudinal Principal Manifold Estimation}\label{alg:two}
\KwData{Data points $\{y_{i, t}\}_{i, t}^{I, T}$, positive integer $d$, positive integer $N_0 < I - 1$, $\alpha$, $\epsilon$, $\epsilon^* \in (0, 1)$, candidate tuning parameters $\{\lambda_k\}_{k=1}^K$, $\{\gamma_l\}_{l=1}^L$, $itr \geq 1$, which is the maximum number of iterations allowed.}
\KwResult{Analytic formula of $g^*: \mathbb{R}^{d+1} \to \mathbb{R}^{D+1}$, optimal tuning parameter $\gamma^*$.}
\For{$t = 1, 2, ... T$}{
    Apply PME algorithm with input $(\{y_{i, t}\}_{i=1}^I, N_0, \alpha, \epsilon, \epsilon^*, \{\lambda_k\}_{k=1}^K)$ and obtain $\{f_t^*\}_{t=1}^T$ and $\{\lambda_t^*\}_{t=1}^T$\;
    Use $\{f_t^*\}_{t=1}^T$ to map a grid of $d$-dimensional parameters $\{r_j\}_{j=1}^N$ to $\{x_{j, t}\}_{j=1}^N$ in $\mathbb{R}^D$\;
}
Apply ISOMAP to parameterize the newly generated collection $\{x_{j, t}\}_{j, t}^{N, T}$ by the $d$-dimensional parameters $\{r_j\}_{j=1}^N$\;
Use parameters $\{r_j\}_{j=1}^N$ and time values $\{t_j\}_{j=1}^N$ to create new
$\pi_{g_{(1)}}(x_{j}) \gets r_j$ for $j=1, ..., N$\;
\For{$l = 1, 2, ..., L$}{
    $\gamma \gets \gamma_l$.\;
    Obtain $g_{(1)}$ by solving 
    $\left(\begin{array}{ccc} 
    2\mathbf{E}\mathbf{W}\mathbf{E} + 2\gamma\mathbf{E} & 2\mathbf{E}\mathbf{W}\mathbf{T} & \mathbf{T} \\
    2\mathbf{T}^T\mathbf{W}\mathbf{E} & 2\mathbf{T}^T\mathbf{W}\mathbf{T} & \mathbf{0} \\
    \mathbf{T}^T & \mathbf{0} & \mathbf{0} \end{array}\right)\left(\begin{array}{c} 
    s_l \\
    \alpha_l \\
    m_l 
    \end{array}\right) = \left(\begin{array}{c}
    2\mathbf{E}\mathbf{W}\mathbf{x} \\
    2\mathbf{T}^T\mathbf{W}\mathbf{x} \\
    \mathbf{0} 
    \end{array}\right)$\;
    $\mathcal{E} \gets 2\epsilon^*$\;
    $n \gets 1$\;
    $\mathcal{D}_{\hat{Q}, N}(g_{(1)}) \gets \sum_{j=1}^N\|x_j - g_{(1)}\|_{\mathbb{R}^{D}}^2$\;
    \While{$\mathcal{E} \geq \epsilon^*$, $n < itr$}{
        Compute $g_{(n + 1)}$ by solving $\left(\begin{array}{ccc} 
        2\mathbf{E}\mathbf{W}\mathbf{E} + 2\gamma\mathbf{E} & 2\mathbf{E}\mathbf{W}\mathbf{T} & \mathbf{T} \\
        2\mathbf{T}^T\mathbf{W}\mathbf{E} & 2\mathbf{T}^T\mathbf{W}\mathbf{T} & \mathbf{0} \\
        \mathbf{T}^T & \mathbf{0} & \mathbf{0} \end{array}\right)\left(\begin{array}{c} 
        s_l \\
        \alpha_l \\
        m_l 
        \end{array}\right) = \left(\begin{array}{c}
        2\mathbf{E}\mathbf{W}\mathbf{x} \\
        2\mathbf{T}^T\mathbf{W}\mathbf{x} \\
        \mathbf{0} 
        \end{array}\right)$\;
        $\mathcal{D}_{\hat{Q}_N}(g_{(n + 1)}) \gets \sum_{j=1}^N\|x_j - g_{(n + 1)}(\pi_{g_{(n + 1)}}(x_j))\|_{\mathbb{R}^D}^2$\;
        $\mathcal{E} \gets |\mathcal{D}_{\hat{Q}_N}(g_{(n + 1)}) - \mathcal{D}_{\hat{Q}_N}(g_{(n)})|/\mathcal{D}_{\hat{Q}_N}(g_{(n)})$\;
        $n \gets n + 1$\;
    }
    $\hat{g}_l \gets g_{(n)}$\;
}
$\kappa \gets \text{max}\{\|\pi_{\hat{g}_{l^*}}(x_j)\|_{\mathbb{R}^d}: j = 1, 2, \dots, I\}$, where $l^* = \arg \min_l\{\frac{1}{N}\sum_{j=1}^N\|x_j - g_{(l)}(\pi_{\hat{g}_{(l)}}(x_j)\|_{\mathbb{R}^D}^2: l = 1, 2, \dots, L\}$\;
$g^*(r) = g^{l^*}(\kappa r)$, where the analytic formula of $g^*$ is from $g_{(n + 1), l}(r) = \sum_{j=1}^N \eta_{4-d}(r - \pi_{g_{(n)}}(x_j)) + \sum_{k=1}^{d + 1} \alpha_{k, l} \times p_k(r)$, and $\gamma^* \gets \gamma_{l^*}$
\end{algorithm}

	\begin{equation}\label{PMSEF}
	\mathcal{K}_{\lambda,\mathbb{P}}(f,g)=\mathbb{E}\left\Vert X_t - f\left(\pi_g(X_t)\right)\right\Vert^2_{\mathbb{R}^D} + \lambda \sum_{t = 1}^T \left\Vert\nabla^{\otimes 2} f(t)\right\Vert_{L^2(\mathbb{R}^d)}^2 + \gamma \sum_{X} \left\Vert\nabla^{\otimes 2} f(X_t)\right\Vert_{L^2(\mathbb{R})}^2, 
	\end{equation}
	\begin{equation}\nonumber
	\mathcal{K}_{\lambda,\mathbb{P}}(f)=\mathcal{K}_{\lambda,\mathbb{P}}(f,f),
	\end{equation}
	where $\Vert\nabla^{\otimes 2}f \Vert_{L^2(\mathbb{R}^d)}^2 = \sum_{l=1}^D\int_{\mathbb{R}^d} \sum_{i,j=1}^d\vert\frac{\partial^2 f_l}{\partial t_i \partial t_j}(t)\vert^2dt$. A manifold $M_{f^*}^d$ determined by $f^*$ is called a principal manifold for $X$ (or $\mathbb{P}$) with the tuning parameter $\lambda$ if 
	\begin{align}\label{def: PM}
	f^*=\arg\min_{f\in\mathscr{F}(\mathbb{P})}\mathcal{K}_{\lambda,\mathbb{P}}(f),\ \ \mbox{ where }\mathscr{F}(\mathbb{P}):=\left\{f\in C_\infty\cap \nabla^{-\otimes 2}L^2( R^d \rightarrow R^D):\sup_{x\in supp(\mathbb{P})}\left\Vert\pi_f(x)\right\Vert_{R^d} = 1 \right\}.
	\end{align}

>>>>

%\RequirePackage[numbers]{natbib}
\RequirePackage[authoryear]{natbib}%% uncomment this for author-year citations
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}%% uncomment this for coloring bibliography citations and linked URLs
\RequirePackage{graphicx}%% uncomment this for including figures

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage[perpage,symbol*]{footmisc}
\usepackage{float}
\usepackage{hyperref}
\usepackage{color}  
\usepackage{tikz}

@@

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

The notation below is used to build to a definition of principal manifolds [still need to formally write out]:
\begin{itemize}
  \item Observed data $\left\{x_i\right\}_{i=1}^I \subset \mathbb{R}^D$
  \item Associated latent parameterizations $\left\{t_i\right\}_{i=1}^I \subset \mathbb{R}^d$ [may change this notation to allow for time points]
  \item $C_{\infty}\left(\mathbb{R}^d \to \mathbb{R}^D\right) = \left\{f \in C(\mathbb{R}^d \to \mathbb{R}^D): \lim_{\|t\|_{\mathbb{R}^d} \to \infty} \|f(t)\|_{\mathbb{R}^D} = \infty\right\}$ 
  \item $\nabla f$ denotes the gradient of $f$
  \item $\nabla^{\bigotimes 2}f$ denotes the Hessian matrix of $f$
  \item $\|\nabla^{\bigotimes 2}f\|_{\mathbb{R}^{d \times d}} = \left(\sum_{i, j = 1}^{d} |\frac{\partial^2f}{\partial t_i \partial t_j}(t)|^2\right)^{\frac{1}{2}}$
  \item $\|\nabla^{\bigotimes 2}f\|_{L^2(\mathbb{R}^{d})}^2 = \sum_{l = 1}^{D}\|\nabla^{\bigotimes 2}f_l\|_{L^2(\mathbb{R}^{d})}^2 = \sum_{l=1}^{D}\int_{\mathbb{R}^d}\sum_{i,j = 1}^{d}|\frac{\partial^2f_l}{\partial t_i \partial t_j}(t)|^2dt$ represents the total squared curvature of manifold $M_f^{d}$
  \item $\mathcal{K}_{\lambda, \mathbb{P}}(f, g) = \mathbb{E}\|X - f(\pi_{g}(X))\|_{\mathbb{R}^{D}}^2 + \lambda\|\nabla^{\bigotimes 2}f\|_{L^2(\mathbb{R}^{d})}^2$, with $\mathcal{K_{\lambda, \mathbb{P}}}(f) = \mathcal{K}_{\lambda, \mathbb{P}}(f, f)$
  \item A manifold $M_{f^*}^{d}$ determined by $f^*$ is a principal manifold for random $D$-vector $X$ with compact support $\text{supp}(\mathbb{P})$ with the tuning parameter $\lambda$ if \[%
    f_{\lambda}^{*} = \argmin_{f \in \mathcal{F}(\mathbb{P})}\mathcal{K}_{\lambda, \mathbb{P}}(f)
  ,\]%
    where \[%
      \mathcal{F}(\mathbb{P}) = \left\{f \in C_{\infty} \cap \nabla^{-biot 2}L^2(\mathbb{R}^{d} \to \mathbb{R}^{D}): \sup_{x \in \text{supp}(\mathbb{P})}\|\pi_f(x)\|_{\mathbb{R}^{d}} = 1\right\}
    .\]%
  \item $\pi_{f_\lambda^{*}}(X)$ gives a $d$-dimensional parameterization of $X$
\end{itemize}

Given this definition, we now summarize the estimation method provided. This algorithm has three main steps: data reduction, fitting, and tuning. In the reduction step, the HDMDE algorithm is used to summarize the data $\left\{x_i\right\}_{i=1}^{I}$ by points $\left\{\mu_j\right\}_{j=1}^{N}$ with $N \leq I$, and each $\mu_j$ associated with weight $\theta_j$. The fitting stage of the algorithm finds estimated functions 
\[%
  \hat{f}_\lambda = \argmin_f \mathcal{K}_{\lambda, \hat{Q}_N}(f)
,\]%
where 
\[%
  \mathcal{K}_{\lambda, \hat{Q}_N}(f) = \sum_{j = 1}^{N}\theta_j \|\mu_j - f(\pi_f(\mu_j))\|_{\mathbb{R}^{D}}^2 + \lambda\|\nabla^{\bigotimes 2}f\|_{L^2(\mathbb{R}^{d})}^2
\]% 
approximates $\mathcal{K}_{\lambda, \mathbb{P}}(f)$. The tuning stage chooses $\lambda^{*} = \argmin_{\lambda > 0}(\mathcal{D}(\hat{f}_\lambda))$, where 
\[%
  \mathcal{D}(\hat{f}_\lambda) = \frac{1}{I}\sum_{i=1}^{I}\|x_i - \hat{f}_\lambda(\pi_{\hat{f}_\lambda}(x_i))\|_{\mathbb{R}^{D}}^2
.\]%

@@

We now introduce the proposed longitudinal principal manifold estimation (LPME) algorithm, following a similar setting as Meng and Eloyan (2021). Let

Outline:
\begin{enumerate}
    \item Show updated loss function for LPME algorithm
    \item LPME algorithm
\end{enumerate}

\begin{algorithm}
\caption{Longitudinal Principal Manifold Estimation}\label{alg:two}
\KwData{Data points $\{y_{i, t}\}_{i, t}^{I, T}$, positive integer $d$, positive integer $N_0 < I - 1$, $\alpha$, $\epsilon$, $\epsilon^* \in (0, 1)$, candidate tuning parameters $\{\lambda_k\}_{k=1}^K$, $\{\gamma_l\}_{l=1}^L$, $itr \geq 1$, which is the maximum number of iterations allowed.}
\KwResult{Analytic formula of $g^*: \mathbb{R}^{d+1} \to \mathbb{R}^{D+1}$, optimal tuning parameter $\gamma^*$.}
\For{$t = 1, 2, ... T$}{
    Apply PME algorithm with input $(\{y_{i, t}\}_{i=1}^I, N_0, \alpha, \epsilon, \epsilon^*, \{\lambda_k\}_{k=1}^K)$ and obtain $\{f_t^*\}_{t=1}^T$ and $\{\lambda_t^*\}_{t=1}^T$\;
    Use $\{f_t^*\}_{t=1}^T$ to map a grid of $d$-dimensional parameters $\{r_j\}_{j=1}^N$ to $\{x_{j, t}\}_{j=1}^N$ in $\mathbb{R}^D$\;
}
Apply ISOMAP to parameterize the newly generated collection $\{x_{j, t}\}_{j, t}^{N, T}$ by the $d$-dimensional parameters $\{r_j\}_{j=1}^N$\;
Use parameters $\{r_j\}_{j=1}^N$ and time values $\{t_j\}_{j=1}^N$ to create new
$\pi_{g_{(1)}}(x_{j}) \gets r_j$ for $j=1, ..., N$\;
\For{$l = 1, 2, ..., L$}{
    $\gamma \gets \gamma_l$.\;
    Obtain $g_{(1)}$ by solving 
    $\left(\begin{array}{ccc} 
    2\mathbf{E}\mathbf{W}\mathbf{E} + 2\gamma\mathbf{E} & 2\mathbf{E}\mathbf{W}\mathbf{T} & \mathbf{T} \\
    2\mathbf{T}^T\mathbf{W}\mathbf{E} & 2\mathbf{T}^T\mathbf{W}\mathbf{T} & \mathbf{0} \\
    \mathbf{T}^T & \mathbf{0} & \mathbf{0} \end{array}\right)\left(\begin{array}{c} 
    s_l \\
    \alpha_l \\
    m_l 
    \end{array}\right) = \left(\begin{array}{c}
    2\mathbf{E}\mathbf{W}\mathbf{x} \\
    2\mathbf{T}^T\mathbf{W}\mathbf{x} \\
    \mathbf{0} 
    \end{array}\right)$\;
    $\mathcal{E} \gets 2\epsilon^*$\;
    $n \gets 1$\;
    $\mathcal{D}_{\hat{Q}, N}(g_{(1)}) \gets \sum_{j=1}^N\|x_j - g_{(1)}\|_{\mathbb{R}^{D}}^2$\;
    \While{$\mathcal{E} \geq \epsilon^*$, $n < itr$}{
        Compute $g_{(n + 1)}$ by solving $\left(\begin{array}{ccc} 
        2\mathbf{E}\mathbf{W}\mathbf{E} + 2\gamma\mathbf{E} & 2\mathbf{E}\mathbf{W}\mathbf{T} & \mathbf{T} \\
        2\mathbf{T}^T\mathbf{W}\mathbf{E} & 2\mathbf{T}^T\mathbf{W}\mathbf{T} & \mathbf{0} \\
        \mathbf{T}^T & \mathbf{0} & \mathbf{0} \end{array}\right)\left(\begin{array}{c} 
        s_l \\
        \alpha_l \\
        m_l 
        \end{array}\right) = \left(\begin{array}{c}
        2\mathbf{E}\mathbf{W}\mathbf{x} \\
        2\mathbf{T}^T\mathbf{W}\mathbf{x} \\
        \mathbf{0} 
        \end{array}\right)$\;
        $\mathcal{D}_{\hat{Q}_N}(g_{(n + 1)}) \gets \sum_{j=1}^N\|x_j - g_{(n + 1)}(\pi_{g_{(n + 1)}}(x_j))\|_{\mathbb{R}^D}^2$\;
        $\mathcal{E} \gets |\mathcal{D}_{\hat{Q}_N}(g_{(n + 1)}) - \mathcal{D}_{\hat{Q}_N}(g_{(n)})|/\mathcal{D}_{\hat{Q}_N}(g_{(n)})$\;
        $n \gets n + 1$\;
    }
    $\hat{g}_l \gets g_{(n)}$\;
}
$\kappa \gets \text{max}\{\|\pi_{\hat{g}_{l^*}}(x_j)\|_{\mathbb{R}^d}: j = 1, 2, \dots, I\}$, where $l^* = \argmin_l\{\frac{1}{N}\sum_{j=1}^N\|x_j - g_{(l)}(\pi_{\hat{g}_{(l)}}(x_j)\|_{\mathbb{R}^D}^2: l = 1, 2, \dots, L\}$\;
$g^*(r) = g^{l^*}(\kappa r)$, where the analytic formula of $g^*$ is from $g_{(n + 1), l}(r) = \sum_{j=1}^N \eta_{4-d}(r - \pi_{g_{(n)}}(x_j)) + \sum_{k=1}^{d + 1} \alpha_{k, l} \times p_k(r)$, and $\gamma^* \gets \gamma_{l^*}$
\end{algorithm}

@@

	\begin{equation}\label{PMSEF}
	\mathcal{K}_{\lambda,\mathbb{P}}(f,g)=\mathbb{E}\left\Vert X_t - f\left(\pi_g(X_t)\right)\right\Vert^2_{\mathbb{R}^D} + \lambda \sum_{t = 1}^T \left\Vert\nabla^{\otimes 2} f(t)\right\Vert_{L^2(\mathbb{R}^d)}^2 + \gamma \sum_{X} \left\Vert\nabla^{\otimes 2} f(X_t)\right\Vert_{L^2(\mathbb{R})}^2, 
	\end{equation}
	\begin{equation}\nonumber
	\mathcal{K}_{\lambda,\mathbb{P}}(f)=\mathcal{K}_{\lambda,\mathbb{P}}(f,f),
	\end{equation}
	where $\Vert\nabla^{\otimes 2}f \Vert_{L^2(\mathbb{R}^d)}^2 = \sum_{l=1}^D\int_{\mathbb{R}^d} \sum_{i,j=1}^d\vert\frac{\partial^2 f_l}{\partial t_i \partial t_j}(t)\vert^2dt$. A manifold $M_{f^*}^d$ determined by $f^*$ is called a principal manifold for $X$ (or $\mathbb{P}$) with the tuning parameter $\lambda$ if 
	\begin{align}\label{def: PM}
	f^*=\argmin_{f\in\mathscr{F}(\mathbb{P})}\mathcal{K}_{\lambda,\mathbb{P}}(f),\ \ \mbox{ where }\mathscr{F}(\mathbb{P}):=\left\{f\in C_\infty\cap \nabla^{-\otimes 2}L^2( R^d \rightarrow R^D):\sup_{x\in supp(\mathbb{P})}\left\Vert\pi_f(x)\right\Vert_{R^d} = 1 \right\}.
	\end{align}
